Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-10-30 manuscript.Rmd
add sem trees

<!--the current goal of preregistration is confirmation-->
One goal of preregistration that has received widespread attention is to clearly distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012; @simmonsPreregistrationWhyHow2021; @bakkerEnsuringQualitySpecificity2020].
In such a narrative, preregistration is justified by a confirmatory research agenda.
However, two problems become apparent under closer inspection.
First, many researchers do not subscribe to a purely confirmatory research agenda [@tukeyExploratoryDataAnalysis1972; @baumeisterChartingFutureSocial2016; @finkelReplicabilityOtherFeatures2017].
Second, there is no strict mapping of the categories preregistered vs. non-preregistered onto the categories confirmatory vs. exploratory research.

>>>>

<!--the current goal of preregistration is confirmation-->
One goal of preregistration that has received widespread attention is to clearly distinguish confirmatory from exploratory research [@mellorEasyPreregistrationWill2018; @nosekPreregistrationRevolution2018; @wagenmakersAgendaPurelyConfirmatory2012; @simmonsPreregistrationWhyHow2021; @bakkerEnsuringQualitySpecificity2020].
In such a narrative, preregistration is justified by a confirmatory research agenda.
However, two problems become apparent under closer inspection.
First, many researchers do not subscribe to a purely confirmatory research agenda [@tukeyExploratoryDataAnalysis1972; @baumeisterChartingFutureSocial2016; @finkelReplicabilityOtherFeatures2017; @brandmaierStructuralEquationModel2013].
Second, there is no strict mapping of the categories preregistered vs. non-preregistered onto the categories confirmatory vs. exploratory research.
